Notes on Control Plane Inference

### 2021-05-28 inference.tex
fix projections

\paragraph{Expressions}
The semantics of expressions is shown in Figure~\label{fig:sem-expr}. Note that
here we implicitly use the strict semantics for definedness, that is, operators
only succeed when all of their arguments are defined, otherwise it returns
undefined.

@@

\begin{definition}[Projections]
  For a set of variables $S \subseteq \Var$, and a packet $\pkt$, write
  $\pkt|_S$ to be projection of $\pkt$ onto $S$. \todo{I guess this means
    packets are partial functions?} Formally,
  \[\pkt|_S \triangleq \{x \mapsto \pkt(x) \mid x \in S\}.\]
  Two packets $\pkt$, $\pkt'$ are equivalent up to $S \subseteq \Var$, written
  $\pkt =_S \pkt'$, iff $\pkt|_S = \pkt'|_s$. A set of packets $P$ is a subset
  of $P'$ up to $S$, written $P \subseteq_S P'$ iff for every packet $\pkt \in
  P$, there exists $\pkt' \in P'$ such that $\pkt =_S \pkt'$. Two sets of
  packets $P$ and $P'$ are $S$-equivalent, written $P =_S P'$ iff $P \subseteq_S
  P'$ and $P \subseteq_S P'$. A set $P \subseteq \Pkt$ is a $V$-equivalence
  class if $\forall \pkt_1, \pkt_2 \in P$, $\pkt_1 =_V \pkt_2$.
\end{definition}

\begin{lemma}[Projection Union-Distributivity]
  \label{lem:proj-union-set}
  For all $P,Q \subseteq \Pkt$, $V \subseteq \Var$,
  $(P\cup Q)|_V = P|_V \cup Q|_V$
\end{lemma}

\begin{proof}
  Let $P,Q \subseteq \Pkt$ and $V \subseteq \Var$ be given. Compute:

  \[\begin{array}{ll}
  (P\cup Q)|_V\\
  = \{\pkt|_V \mid \pkt \in P\cup Q\}\\
  = \{\pkt|_V \mid \pkt \in P\}\cup \{\pkt|_V \mid \pkt \in Q\}\\
  = P|_V \cup Q|_V
  \end{array}\]
\end{proof}

\begin{lemma}[Projection Idempotence]
  \label{lem:proj-idem}
  For all $\pkt \in \Pkt$, $V \subseteq \Var$,
  $(\pkt|_V)|_V = \pkt|_V$
\end{lemma}

\begin{proof}
  Let $\pkt \in \Pkt$ and $V \subseteq \Var$ be given.
  \[\begin{array}{ll}
    (\pkt|_V)|_V \\
    = \{x \mapsto (\pkt|_V)(x) \mid x \in V\} & \text{by definition}\\
    = \{x \mapsto (\{y \mapsto \pkt(y) \mid y \in V\})(x) \mid x \in V\} & \text{by definition}\\
    = \{x \mapsto \pkt(x) \mid x \in V\} & \beta\text{-reduction}\\
    = \pkt|_V & \text{by definition}
  \end{array}\]
\end{proof}

\begin{lemma}[Projection Idempotence for Sets]
  \label{lem:proj-idem-set}
  For all $P \subseteq \Pkt$, $V \subseteq \Var$,
  $(P|_V)|_V = P|_V$
\end{lemma}

\begin{proof}
  Let $P \subseteq \Pkt$ and $V \subseteq \Var$ be given. Compute:
  \[\begin{array}{ll}
  (P|_V)|_V \\
  = \{\pkt|_V \mid \pkt \in P|_V\}
  & \text{by definition of } (\cdot)|_V : \mathcal{P}(\Pkt) \to \mathcal{P}(\Pkt) \\
  = \{\pkt|_V \mid \pkt \in \{\pkt'|_V \mid \pkt'\in P\}\}
  & \text{by definition of } (\cdot)|_V : \mathcal{P}(\Pkt) \to \mathcal{P}(\Pkt) \\
  = \{(\pkt|_V)|_V \mid \pkt \in P \}
  & \text{by set theory} \\
  = \{\pkt|_V \mid \pkt \in P\} & \text{by Lemma~\ref{lem:proj-idem}} \\
  = P|_V & \text{by definition of } (\cdot)|_V : \mathcal{P}(\Pkt) \to \mathcal{P}(\Pkt)
  \end{array}\]
\end{proof}

@@

\begin{corollary}[Subset Implies Projected Subset]
  \label{lem:subset-proj}
  For $P,Q \subseteq \Pkt$, and $ V \subseteq \Var$,
  If $P \subseteq Q$ then $P \subseteq_V Q$.
\end{corollary}

\begin{lemma}[Subset Projection Equality]
  \label{lem:subset-proj-equal}
  For $P,Q \subseteq \Pkt$ and $U \subseteq V \subseteq \Var$,
  If $P =_V Q$, then $P =_U Q$.
\end{lemma}

\begin{proof}
  Let $P$,$Q$,$U$,$V$ be given as above. Assume $P =_V Q$. Show $P =_U Q$. Let
  $\pkt \in P$. Since $P =_V Q$, we know that $P \subseteq_V Q$ and $Q
  \subseteq_V P$. By Lemma~\ref{lem:subset-proj-subset},$P \subseteq_U Q$ and $Q
  \subseteq_U P$. Conclude $P =_U Q$.
\end{proof}

\begin{corollary}[Equality Implies Projected Equality]
  \label{lem:equal-proj}
  For $P,Q \subseteq \Pkt$, and $ V \subseteq \Var$, If $P = Q$ then $P =_V Q$.
\end{corollary}

\begin{lemma}[Union Packet Projection]
  \label{lem:union-pkt-proj}
  For $\pkt_1,\pkt_2 \in \Pkt$, and $U, V \subseteq \Pkt$, if $\pkt_1 =_U
  \pkt_2$ and $\pkt_1 =_V \pkt_2$, then $\pkt_1 =_{U \cup V} \pkt_2$.
\end{lemma}

\begin{proof}
  Let $\pkt_1$, $\pkt_2$, $U$, $V$ be given as above. Assume $\pkt_1 =_U \pkt_2$
  and $\pkt_1 =_V \pkt_2$. Let $x \in U \cup V$. There are two cases. If $x \in
  U$, the assumption $\pkt_1 =_U \pkt_2 $ gives $\pkt_1(x) = \pkt_2(x)$.
  Conversely if $x \in V$, the assumption $\pkt_1 =_V \pkt_2$ gives $\pkt_1(x) =
  \pkt_2(x)$. Conclude $\pkt_1 =_{U \cup V} \pkt_2$.
\end{proof}

\begin{lemma}[Expression Projection]
  \label{lem:proj-expr}
  For every set of variables $V \subseteq \Var$, packet $\pkt \in \Pkt$ and
  expression $e \in \BVExpr$, such that $\efvs(e) \subseteq V$, $\edenote{e}\pkt =
  \edenote{e}(\pkt|_V)$.
\end{lemma}
\begin{proof}
  Let $V \subseteq \Var$ be given.
  Proceed by induction on $e$, leaving $\pkt$ arbitrary.
  \begin{enumerate}[align=left]
  \item[($e = v$)] Let $\pkt$ be given. $\edenote{v}\pkt = v = \edenote{v}{\pkt|_V}$
  \item[($e = x$)] Let $\pkt$ be given. Note that $\efvs(x) = \{x\} \subseteq V$. Compute:
    \[\begin{array}{ll}
    \edenote{x}(\pkt|_V) \\
    = (\pkt|_V)(x)
    & \text{by definition of }\edenote\cdot\\
    = \{y \mapsto \pkt(y) \mid y \in V\}(x)
    & \text{by definition of }(\cdot)|_V : \Pkt \to \Pkt\\
    = \pkt(x) & \text{since } x \in V
    \end{array}
    \]
  \item[($e = e_1 \binop e_2$)] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \edenote{e_1 \binop e_2}\pkt \\
    = \edenote{e_1}\pkt \binop \edenote{e_2}\pkt & \text{definition of }\edenote\cdot \\
    = \edenote{e_1}(\pkt|_V) \binop \edenote{e_2}(\pkt|_V) & \text{by IHS since }\efvs(e_i) \subseteq \efvs(e_1 \binop e_2) \subseteq V, i = 1,2 \\
    = \edenote{e_1 \binop e_2}(\pkt|_V) & \text{definition of }\edenote\cdot
    \end{array}\]
  \item[($e = \unop e$)] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \edenote{\unop e}\pkt \\
    = \unop \edenote{e}\pkt & \text{definition of }\edenote\cdot \\
    = \unop \edenote{e}(\pkt|_V) & \text{by IH, since } \efvs(e) = \efvs(\unop e) \subseteq V \\
    = \edenote{\unop e}(\pkt|_V) & \text{definition of }\edenote\cdot
    \end{array}\]
  \end{enumerate}
\end{proof}

\begin{lemma}[Satisfaction Projection]
  \label{lem:proj-satis}
  For every set of variables $V \subseteq \Var$, packet $\pkt \in \Pkt$ and
  boolean expression $b \in \BExpr$, such that $\bfvs(b) \subseteq V$,
  $\pkt \models b$ iff $\pkt|_V \models b$.
\end{lemma}

\begin{proof}
  Let $V \subseteq \Var$ be given.
  Proceed by induction on $b$, leaving $\pkt$ arbitrary.
  \begin{enumerate}[align=left]
  \item[($b = \FALSE$)] Immediate.
  \item[($b = b_1 \Rightarrow b_2$)]
    Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \pkt \models b_1 \Rightarrow b_2 \\
    \iff \pkt \not\models b_1 \text{or} \pkt\models b_2 & \text{by definition of } \models   \\
    \iff \pkt|_V \not\models b_1 \text{or} \pkt|_V \models b_2  & \text{by IHs, since} \bfvs(b_i) \subseteq \bfvs(b_1 \Rightarrow b_2) \subseteq V, i = 1,2  \\
    \iff \pkt|_V \models b_1 \Rightarrow b_2
    & \text{by definition of } \models
    \end{array}\]

  \item[($b = e_1 = e_2$)] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \pkt \models e_1 = e_2 \\
    \iff \edenote{e_1}\pkt = \edenote{e_2}\pkt
    & \text{by definition of }\models \\
    \iff \edenote{e_1}(\pkt|_V) = \edenote{e_2}(\pkt|_V)
    & \text{by Lemma~\ref{lem:proj-expr}, since } \efvs(e_i) \subseteq \bfvs(e_1 = e_2) \subseteq V, i = 1,2 \\
    \iff \pkt|_V \models e_1 = e_2
    & \text{by definition of }\models
    \end{array}\]

  \end{enumerate}

\begin{lemma}[Projection-Denotation Commutativity]
  \label{lem:proj-den-comm}
  For a closed action $c \in \Cmd$, $\fvs(c) \subseteq V \subseteq \Var$ and
  $\pkt \in \Pkt$, $\denote{c} \pkt =_V \denote{c} \pkt|_V$.
\end{lemma}

\begin{proof}
  Proceed by induction on $c$, leaving $\pkt$ general.
  \begin{enumerate}[align=left]
  \item[$(c = x:=e)$] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    (\denote{x:=e} (\pkt|_V))|_V\\
    = ((\pkt|_V)\{x:=\edenote{e}(\pkt|_V)\})|_V
    & \text{definition} \\
    = ((\pkt|_V)\{x := \edenote{e}\pkt\})|_V
    & \text{By Lemma~\ref{lem:proj-expr} since } \fvs(e) \subseteq \fvs(x := e) \subseteq V \\
    = (\pkt\{x := \edenote{e}\pkt\}|_V)|_V
    & \text{since } x \in \fvs(x:=e) \subseteq V \\
    = ((\denote{x:=e}\pkt)|_V)|_V
    & \text{by definition of }\denote{\cdot}\\
    = (\denote{x:=e}\pkt)|_V
    & \text{by Lemma~\ref{lem:proj-idem}}
    \end{array}\]
    The result follows by definition of $=_V$.

  \item[$(c = \havoc x)$] Contradictory; $\havoc x$ is not an action.
  \item[$(c = \assume b)$]
    Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    (\denote{\assume b} \pkt)|_V \\
    = (\{\pkt \mid \pkt \models b\})|_V
    & \text{definition of}\denote\cdot\\
    = ((\{\pkt \mid \pkt \models b\})|_V)|_V
    & \text{By Lemma~\ref{lem:proj-idem-set}} \\
    = (\{\pkt|_V \mid \pkt \models b\})|_V
    & \text{definition of }(\cdot)|_V : \mathcal P (\Pkt) \to \mathcal P (\Pkt) \\
    = (\{\pkt|_V \mid \pkt|_V \models b\})|_V
    & \text{By Lemma~\ref{lem:proj-satis} since } \fvs(b) \subseteq \fvs(\assume b) \subseteq V \\
    = (\denote{\assume b}(\pkt|_V))|_V
    & \text{by definition of}\denote\cdot
    \end{array}
    \]
    The result follows by definition of $=_V$.

  \item[$(c = \assert b)$] \textit{sim.}
  \item[$(c = c_1;c_2)$] Let $\pkt$ be given. Compute:
    \[\begin{array}{>{\displaystyle}ll}
    (\denote{c_1;c_2}\pkt)|_V \\
    = (\denote{c_2}^\dagger(\denote{c_1}\pkt))|_V
    & \text{definition of }\denote\cdot \\
    = \left(\bigcup_{\pkt' \in \denote{c_1} \pkt} \denote{c_2}\pkt'\right)|_V
    & \text{definition of }(\cdot)^\dagger \\
    = \bigcup_{\pkt' \in \denote{c_1} \pkt} (\denote{c_2}\pkt')|_V
    & \text{by Lemma~\ref{lem:proj-union-set}} \\
    = \bigcup_{\pkt' \in \denote{c_1}\pkt} (\denote{c_2}(\pkt'|_V))|_V
    & \text{IH}(c_2)  \\
    =\bigcup_{\pkt' \in (\denote{c_1}\pkt)|_V} (\denote{c_2} \pkt')|_V
    & \text{by set theory} \\
    = \bigcup_{\pkt' \in (\denote{c_1}(\pkt|_V))|_V} (\denote{c_2} \pkt')|_V
    & \text{by IH}(c_1) \\
    = \bigcup_{\pkt' \in \denote{c_1}(\pkt|_V)} (\denote{c_2} (\pkt'|_V))|_V
    & \text{by set theory} \\
    = \bigcup_{\pkt' \in \denote{c_1}(\pkt|_V)} ((\denote{c_2} \pkt')|_V)|_V
    & \text{by IH}(c_2) \\
    = \bigcup_{\pkt' \in \denote{c_1}(\pkt|_V)} (\denote{c_2} \pkt')|_V
    & \text{by Lemma~\ref{lem:proj-idem-set}} \\
    = \left(\bigcup_{\pkt' \in \denote{c_1}(\pkt|_V)} \denote{c_2}\pkt'\right)|_V
    & \text{by Lemma~\ref{lem:proj-union-set}} \\
    = \denote{c_2}^\dagger(\denote{c_1}(\pkt|_V))|_V
    & \text{By definition of }(\cdot)^\dagger\\
    = (\denote{c_1;c_2}(\pkt|_V))|_V
    & \text{By definition of }\denote\cdot
    \end{array}\]
    The result follows by definition of $=_V$.

  \item[$(c = c_1 \choice c_2)$] Let $\pkt$ be given.
    \[\begin{array}{ll}
    (\denote{c_1\choice c_2}\pkt)|_V \\
    = (\denote{c_1}\pkt \cup \denote{c_2}\pkt)|_V
    & \text{By definition of }\denote\cdot \\
    = (\denote{c_1}\pkt)|_V \cup (\denote{c_2}\pkt)|_V
    & \text{By Lemma~\ref{lem:proj-union-set}} \\
    = (\denote{c_1}(\pkt|_V))|_V \cup (\denote{c_2}(\pkt|_V))|_V
    & \text{By IHs} \\
    = ((\denote{c_1}(\pkt|_V) \cup \denote{c_2}(\pkt|_V))|_V)|_V
    & \text{By Lemma~\ref{lem:proj-union-set}} \\
    = (\denote{c_1}(\pkt|_V) \cup \denote{c_2}(\pkt|_V))|_V
    & \text{By Lemma~\ref{lem:proj-idem-set}}\\
    = (\denote{c_1 \choice c_2}(\pkt|_V))|_V
    & \text{By definition of }\denote\cdot \\
    \end{array}\]

    The result follows by definition of $=_V$.

  \item[$(c = t.\apply())$] Contradictory; $t.\apply()$ is not an action.
  \end{enumerate}

@@

\begin{lemma}[Unused Variable Noninterference]
  \label{lem:param-noninter}
  For $c \in \Cmd$, $\sigma : \State$, $\pkt \in \Pkt$,
  $\{v_1,v_2\} \subseteq \Value$, $y \in \Var \setminus \fvs(c)$,
  $\denote{c}^\sigma \pkt\{y \mapsto v\} =_{\Var \setminus \{y\}}\denote{c}^\sigma\pkt\{y \mapsto v\}$.
\end{lemma}

@@

    The result follows by Lemma~\ref{lem:equal-proj}.

@@

        \item[\textit{Case 2}.] Assume there is no $r \in \sigma(t)$ such that
          $\pkt\{y \mapsto v_1\} \models t.\matchrow(r)$. Then by
          Lemma~\ref{lem:bool-noninter}, there is now $r \in \sigma(t)$ such
          that $\pkt\{y \mapsto v_2\} \models t.\matchrow(r)$. Then by definitions:
          \[\denote{t.\apply()}^\sigma \pkt\{y \mapsto v_1\} = \{\pkt\{y \mapsto v_1\}\} = \{\pkt\{y \mapsto v_2\}\} = \denote{t.\apply()}^\sigma \pkt\{y \mapsto v_2\}\]
          The result follows by Lemma~\ref{lem:equal-proj}.
      \end{enumerate}

@@

\begin{lemma}[Unused Variable Set Noninterference]
  \label{lem:param-noninter-set}
  For $c \in \Cmd$, $\sigma : \State$, $\pkt \in \Pkt$,
  $\{v_1,v_2\} \subseteq \Value$, $Y \subseteq \Var \setminus \fvs(c)$,
  $\denote{c}^\sigma \pkt\{y \mapsto v\} =_{\Var \setminus Y}\denote{c}^\sigma\pkt\{y \mapsto v\}$.
\end{lemma}

@@

  \multicolumn{3}{l}{\state\sigma_T \in \BExpr} \\
  \state\sigma_T &\triangleq
  & \displaystyle\bigwedge_{ t \in T } \state\sigma^t
  \end{array}
  \]
  \caption{Symbolic State Encoding. Where $T \subseteq \Table$. We write
    $\state\sigma_c$ where $c \in \Cmd$ as shorthand for $\state\sigma_{\tables(c)}$.}
  \label{fig:table-instrument}
\end{figure}

@@

\begin{proof}
  Proceed by induction on $c$.
  \begin{enumerate}[align=left]
  \item[$(c = x:=e)$] Immediate, since $R = \emptyset = G$, $\assume{\state\sigma}_{x:=e} = \TRUE$, and $(x:=e)\instr = (x:=e)$.
  \item[$(c = \havoc x)$] \textit{sim}.
  \item[$(c = \assume b)$] \textit{sim}.
  \item[$(c = \assert b)$] \textit{sim}.
  \item[$(c = c_1;c_2)$] Note that well-formedness\todo{define well formedness as single-use tables} implies $\tables(c_1) \cap
    \tables(c_2) = \emptyset$. Let $T_2 = \tables(c_2)$ and $T_1 = T \setminus
    T_2$. Let $R_2 = \{\rho_t.* \mid t \in T_2\}$ and $R_1 = R \setminus R_2$.
    Let $G_2 = \{\rho_t.* \mid t \in T_2\}$ and $G_1 = G \setminus G_2$. Compute
    as follows:
    \[\begin{array}{ll}
    \denote{\havoc {R \cup G}; \assume{\state\sigma_{T}};(c_1;c_2)\instr}\,\pkt
    & \\
    = \denote{\havoc{R\cup G}; \assume{\state\sigma_{T}}; c_1\instr;c_2\instr}\,\pkt
    & \text{definition of }(\cdot)\instr \\
    = \denote{\havoc{R\cup G}; \assume{\state\sigma_{T_1}};\assume{\state\sigma_{T_2}};c_1\instr;c_2\instr}\,\pkt
    & \text{By Lemmas~\ref{lem:sigma-distrib-seq} \&~\ref{lem:assume-currying}} \\
    = \denote{\havoc{R_1 \cup G_1}; \havoc{R_2 \cup G_2}; \assume{\state\sigma_{T_1}};\assume{\state\sigma_{T_2}};c_1\instr;c_2\instr}\,\pkt
    & \text{By definition } \\
    = \denote{\havoc{R_1\cup G_1}; \havoc{R_2 \cup G_2}; \assume{\state\sigma_{T_1}};c_1\instr;\assume{\state\sigma_{T_2}};c_2\instr}\,\pkt
    & \text{By Lemma~\ref{lem:disj-comm} and } \tables(c_1) \cap \tables(c_2) = \emptyset \\
    = \denote{(\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr);
      (\havoc{R_2 \cup G_2};\assume{\state\sigma_{T_2}};c_2\instr)}\,\pkt
    & \text{By Lemma~\ref{lem:disj-comm} and } \tables(c_1) \cap \tables(c_2) = \emptyset\\
    = \denote{\havoc{R_2 \cup G_2};\assume{\state\sigma_{T_2}};c_2\instr}^\dagger
    \left(\denote{\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr}\,\pkt\right)
    & \text{by definition} \\
    =_V {\denote{c_2}^\sigma}^\dagger \left(\denote{\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr}\,\pkt\right)
    & \text{by IH}(c_2) \text{ since } \fvs(c_2) \subseteq \fvs(c_1;c_2) \subseteq V \\
    =_V {\denote{c_2}^\sigma}^\dagger \left({\denote{c_1}^\sigma}^\dagger\pkt\right)
    & \text{by IH}(c_1) \text{ since } \fvs(c_1) \subseteq \fvs(c_1;c_2) \subseteq V \\
    = \denote{c_1;c_2}^\sigma\pkt
    & \text{by definition of }\denote{-}^\sigma\\
    \end{array}\]

    The result follows by Lemma~\ref{lem:equal-proj}.

@@

       which is $V$-equivalent to
       $\denote{t.\action[r_i.\action](r_i.\data)}\,\pkt$ by
       Lemma~\ref{lem:proj-den-comm}. The result follows by the IH on
       $t.\action[r_i.\action](r_i.\data)$ and Lemma~\ref{lem:equal-proj}.

@@

        Our assumption gives us that $\bigwedge_{j=1}^n \neg t.\matchrow(r_j)$,
        which means that $\gamma_t.\hitAction > n$, and that $\gamma_t.\miss =
        1$. Conclude that $H_a = \emptyset$ and $M \neq \emptyset$. Since
        $\emptyset \neq M \subseteq P =_V \{\pkt\}$, $M =_V \{\pkt\}$ by
        Lemma~\ref{lem:subset-proj}. The result follows by
        Lemma~\ref{lem:equal-proj}.
    \end{enumerate}

>>>>

\paragraph{Expressions}
The semantics of expressions is shown in Figure~\ref{fig:sem-expr}. Note that
here we implicitly use the strict semantics for definedness, that is, operators
only succeed when all of their arguments are defined, otherwise it returns
undefined.

@@

\begin{definition}[Projections]
 Two packets $\pkt$, $\pkt'$ are equivalent up to $V \subseteq \Var$, written
 $\pkt =_V \pkt'$, iff $\forall x \in V \pkt(x) = \pkt'(x)$. A set of packets
 $P$ is a subset of $P'$ up to $S$, written $P \subseteq_S P'$ iff for every
 packet $\pkt \in P$, there exists $\pkt' \in P'$ such that $\pkt =_S \pkt'$.
 Two sets of packets $P$ and $P'$ are $S$-equivalent, written $P =_S P'$ iff $P
 \subseteq_S P'$ and $P \subseteq_S P'$. A set $P \subseteq \Pkt$ is a
 $V$-equivalence class if $\forall \pkt_1, \pkt_2 \in P$, $\pkt_1 =_V \pkt_2$.
\end{definition}

\begin{remark}
  Standard equality and subset at all of these types is equivalent to projected
  equality/subset on the universal set of variables, i.e. $(=) = (=_\Var)$ and
  $(\subseteq) = (\subseteq_\Var)$.
\end{remark}

@@

\begin{corollary}[Subset Implies Projected Subset]
  \label{cor:subset-proj}
  For $P,Q \subseteq \Pkt$, and $ V \subseteq \Var$,
  If $P \subseteq Q$ then $P \subseteq_V Q$.
\end{corollary}

\begin{lemma}[Subset Projection Equals]
  \label{lem:subset-proj-equals}
  For $P,Q \subseteq \Pkt$ and $U \subseteq V \subseteq \Var$,
  If $P =_V Q$, then $P =_U Q$.
\end{lemma}

\begin{proof}
  Let $P$,$Q$,$U$,$V$ be given as above. Assume $P =_V Q$. By definition we have
  $P \subseteq_V Q$ and $Q \subseteq_V P$. By
  Lemma~\ref{lem:subset-proj-subset}, these become $P \subseteq_U Q$ and $Q\subseteq_U P$
  Conclude $P =_U Q$.
\end{proof}

\begin{corollary}[Equality Implies Projected Equality]
  \label{cor:equal-proj}
  For $P,Q \subseteq \Pkt$, and $ V \subseteq \Var$, If $P = Q$ then $P =_V Q$.
\end{corollary}

\begin{lemma}[Projection-Denotation Commutativity]
  \label{lem:proj-den-comm}
  For an action $c \in \Cmd$, $\fvs(c) \subseteq V \subseteq \Var$ and $\pkt \in \Pkt$,
  if $P =_V Q$, then $\denote{c}^\dagger P =_V \denote{c}^\dagger Q$.
\end{lemma}

\begin{proof}
  By Lemma~\ref{lem:param-noninter-set}
\end{proof}

@@

\begin{lemma}[Unused Variable Noninterference]
  \label{lem:param-noninter}
  For $c \in \Cmd$, $\sigma : \State$, $\pkt \in \Pkt$,
  $v_1,v_2 \in \Value$, $y \in \Var \setminus \fvs(c)$,
  $\denote{c}^\sigma \pkt\{y \mapsto v\} =_{\Var \setminus \{y\}}\denote{c}^\sigma\pkt\{y \mapsto v\}$.
\end{lemma}

@@

    The result follows by Corollary~\ref{cor:equal-proj}.

@@

        \item[\textit{Case 2}.] Assume there is no $r \in \sigma(t)$ such that
          $\pkt\{y \mapsto v_1\} \models t.\matchrow(r)$. Then by
          Lemma~\ref{lem:bool-noninter}, there is now $r \in \sigma(t)$ such
          that $\pkt\{y \mapsto v_2\} \models t.\matchrow(r)$. Then by definitions:
          \[\denote{t.\apply()}^\sigma \pkt\{y \mapsto v_1\} = \{\pkt\{y \mapsto v_1\}\} = \{\pkt\{y \mapsto v_2\}\} = \denote{t.\apply()}^\sigma \pkt\{y \mapsto v_2\}\]
          The result follows by Corollary~\ref{cor:equal-proj}.
      \end{enumerate}

@@

\begin{lemma}[Unused Variable Set Noninterference]
  \label{lem:param-noninter-set}
  For $c \in \Cmd$, $\sigma : \State$, $\pkt \in \Pkt$,
  $V_1,V_2 \subseteq \Value$, $Y \subseteq \Var \setminus \fvs(c)$,
  $\denote{c}^\sigma \pkt\{Y \mapsto V_1\} =_{\Var \setminus Y}\denote{c}^\sigma\pkt\{Y \mapsto V_2\}$.
\end{lemma}

@@

  \multicolumn{3}{l}{\state\sigma_T \in \BExpr} \\
  \state\sigma_T &\triangleq
  & \displaystyle\bigwedge_{ t \in T } \state\sigma^t
  \end{array}
  \]
  \caption{Symbolic State Encoding. Where $T \subseteq \Table$. We write
    $\state\sigma_c$ where $c \in \Cmd$ as shorthand for $\state\sigma_{\tables(c)}$.}
  \label{fig:state-encode}
\end{figure}

@@

\begin{proof}
  Proceed by induction on $c$.
  \begin{enumerate}[align=left]
  \item[$(c = x:=e)$] Immediate, since $R = \emptyset = G$, $\assume{\state\sigma}_{x:=e} = \TRUE$, and $(x:=e)\instr = (x:=e)$.
  \item[$(c = \havoc x)$] \textit{sim}.
  \item[$(c = \assume b)$] \textit{sim}.
  \item[$(c = \assert b)$] \textit{sim}.
  \item[$(c = c_1;c_2)$] Note that well-formedness implies $\tables(c_1) \cap
    \tables(c_2) = \emptyset$. Let $T_2 = \tables(c_2)$ and $T_1 = T \setminus
    T_2$. Let $R_2 = \{\rho_t.* \mid t \in T_2\}$ and $R_1 = R \setminus R_2$.
    Let $G_2 = \{\rho_t.* \mid t \in T_2\}$ and $G_1 = G \setminus G_2$. Compute
    as follows:
    \[\begin{array}{ll}
    \denote{\havoc {R \cup G}; \assume{\state\sigma_{T}};(c_1;c_2)\instr}\,\pkt
    & \\
    = \denote{\havoc{R\cup G}; \assume{\state\sigma_{T}}; c_1\instr;c_2\instr}\,\pkt
    & \text{definition of }(\cdot)\instr \\
    = \denote{\havoc{R\cup G}; \assume{\state\sigma_{T_1}};\assume{\state\sigma_{T_2}};c_1\instr;c_2\instr}\,\pkt
    & \text{By Lemmas~\ref{lem:sigma-distrib-seq} \&~\ref{lem:assume-currying}} \\
    = \denote{\havoc{R_1 \cup G_1}; \havoc{R_2 \cup G_2}; \assume{\state\sigma_{T_1}};\assume{\state\sigma_{T_2}};c_1\instr;c_2\instr}\,\pkt
    & \text{By definition } \\
    = \denote{\havoc{R_1\cup G_1}; \havoc{R_2 \cup G_2}; \assume{\state\sigma_{T_1}};c_1\instr;\assume{\state\sigma_{T_2}};c_2\instr}\,\pkt
    & \text{By Lemma~\ref{lem:disj-comm} and } \tables(c_1) \cap \tables(c_2) = \emptyset \\
    = \denote{(\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr);
      (\havoc{R_2 \cup G_2};\assume{\state\sigma_{T_2}};c_2\instr)}\,\pkt
    & \text{By Lemma~\ref{lem:disj-comm} and } \tables(c_1) \cap \tables(c_2) = \emptyset\\
    = \denote{\havoc{R_2 \cup G_2};\assume{\state\sigma_{T_2}};c_2\instr}^\dagger
    \left(\denote{\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr}\,\pkt\right)
    & \text{by definition} \\
    =_V {\denote{c_2}^\sigma}^\dagger \left(\denote{\havoc{R_1 \cup G_1}; \assume{\state\sigma_{T_1}};c_1\instr}\,\pkt\right)
    & \text{by IH}(c_2) \text{ since } \fvs(c_2) \subseteq \fvs(c_1;c_2) \subseteq V \\
    =_V {\denote{c_2}^\sigma}^\dagger \left({\denote{c_1}^\sigma}^\dagger\pkt\right)
    & \text{by IH}(c_1) \text{ since } \fvs(c_1) \subseteq \fvs(c_1;c_2) \subseteq V \\
    = \denote{c_1;c_2}^\sigma\pkt
    & \text{by definition of }\denote{-}^\sigma\\
    \end{array}\]

    The result follows by Corollary~\ref{cor:equal-proj}.

@@

       which is $V$-equivalent to
       $\denote{t.\action[r_i.\action](r_i.\data)}\,\pkt$ by
       Lemma~\ref{lem:proj-den-comm}, since $H_{r_i.\action} =_v \{\pkt\}$. The result follows by the IH on
       $t.\action[r_i.\action](r_i.\data)$ and Corollary~\ref{cor:equal-proj}.

@@

        Our assumption gives us that $\bigwedge_{j=1}^n \neg t.\matchrow(r_j)$,
        which means that $\gamma_t.\hitAction > n$, and that $\gamma_t.\miss =
        1$. Conclude that $H_a = \emptyset$ and $M \neq \emptyset$. Since
        $\emptyset \neq M \subseteq P =_V \{\pkt\}$, $M =_V \{\pkt\}$ by
        Corollary~\ref{cor:subset-proj}. The result follows by
        Corollary~\ref{cor:equal-proj}.
    \end{enumerate}
